An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-15 EconGrowthSeminar.Rnw
Some changes to the seminar presentation.

\begin{frame}{Example Cobb-Douglas Fit} %----------------------------
<<CDeGammaGraphsZA>>=
  cdeGridGraphs("ZA", "Q")
@
\end{frame}

>>>>

\begin{frame}{Parameter Estimation for Cobb-Douglas With Energy} %----------------------------
  \begin{equation*} \label{eq:CD_With_Energy}
    y = \mathrm{e}^{\lambda (t-t_0)}k^{\alpha}l^{\beta}e^{\gamma}
  \end{equation*}
  \begin{itemize}
    \item{Objective: determine $\lambda$, $\alpha$, $\beta$, and $\gamma$ that best fits data}
    \item{Almost identical to Cobb-Douglas without energy}
    \item{Perform grid search over $\gamma$}
    \item{Re-estimate $\lambda$, $\alpha$, and $\beta$ at each value of $\gamma$}
    \item{Respect sum constraint ($\alpha + \beta + \gamma = 1$)}
  \end{itemize}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{South Africa Cobb-Douglas With Energy} %----------------------------
<<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight, eval=TRUE>>=
  cdeGridGraph("ZA", "Q", textScaling=0.8)
@
\end{frame}
